Same as always: I suck at titles

### 2024-09-16 manuscript/manuscript_eb.Rmd
change typos
there will still be typos :)

Impressions of other people arise naturally and automatically [@ulemanetal2008]. Speakers can be evaluated not only by what they say but how they say it. For example, vocal features of speech can affect perceptions of confidence and persuasion [@guyeretal2019speech], status and solidarity [@pittamgallois198], and even attractiveness [@feinbergetal2005]. One repeatedly reported feature of speech said to bias listeners' evaluations is its fluency. Disfluencies, such as _uh_ or _um_ in English can lead to poorer evaluations of the speaker in terms of intelligence [@christenfeld1995], competence [@nortonhogan1980], and certainty of their own knowledge [@brennanwilliams1995]. Interestingly, speech produced with an accent different from one's own - particularly a _foreign_ accent - can also elicit negative perceptions of the speaker, including worse evaluations in terms of status, solidarity, and credibility [@gluszeketal2011; @gluszekdovidio2010; @rakicetal2011; @levarikeysar2010]. In this study, however, we explore a rather counterintuitive idea: That the co-presence of these two factors (i.e., (dis)fluency and foreign accents) can diminish the negative impact they have individually. It is important to note that it is not our interested whether these cues correlate with a speaker's knowledge or whether listeners believe the speaker to be intentionally misleading: Rather, we are interested in whether, in scenarios where the speaker is expected to be cooperative and knowledgeable, listeners are still biased by irrelevant cues.

There is a growing body of literature showing that listeners speech qualities are taken as reflective of a speaker's knowledgeability. Voices with a slow speech rate, low amplitude and a large F0 range are more likely to be rated as less confident, and produce distinct neural responses [@jiangpell2015; @jiangpell2016a; @jiangpell2016b]. Similarly, prosody guides listeners' evaluations of certainty and honesty cross-linguistically [@goupiletal2021]. These non-verbal qualities of speech may be accompanied by verbal markers of hesitation, such as disfluencies [@shribergetal1997; @shriberglickley1993; @grosjeandeschamps1975; @jiangpell2017]. @brennanwilliams1995 demonstrated that filled pauses (e.g., uh, mm, or um) can be perceived as indices of speakers’ confidence in their knowledge. In their study, participants listened to previously recorded answers to trivia questions (without hearing the questions) and were asked to rate how likely each speaker would be to recognise the correct answer to the question i.e., _feeling of another's knowing_, FOAK. Amongst the cues that biased participants' assessments were filled pauses:  Answers containing a disfluency were more likely to receive lower FOAK ratings, suggesting that filled pauses were taken as reflective of speakers’ reduced certainty about their knowledge. In contrast, non-answers (i.e., 'I don’t know') were more likely to receive a higher FOAK rating if preceded by a filled pause. @brennanwilliams1995 took this as evidence that listeners are sensitive to the surface form of delivery, and in particular, to the cues displayed by speakers when they do not know (or cannot remember at the moment of being asked) the answer to a question [see also @smithclark1993].

Interestingly, who produces the information can also affect how it is evaluated. On the one hand, speakers with an accent different from that of the listeners are more likely to be negatively evaluated (e.g., [@dragojevicgiles2016; @gluszekdovidio2010] and statements produced with a foreign-accent are more likely to receive lower ratings of credibility compared to statements produced with a native accent [@levarikeysar2010; @boduchlevari2021; but cf., @stocker2017; @wetzeletal2021; @barlowetal2024; @souzamarkman2013; @foucartetal2020; @foucarthartsuiker2021]. This divide in evaluations as a function of a speaker's accent has been accounted for in terms of processing fluency [@levarikeysar2010], group membership, and a combination of both [@maihoffmann2014].

Alternatively, but not exclusively, speaker identity in itself can bias interpretation. Specifically, whether a speaker is providing information in their first or second language has been shown to affect that listeners interpret. @fairchildetal2020 asked participants to explain why a native or a non-native speaker had been underinformative in a previously presented story. Native speakers who provided less information than necessary were more likely to be rated as unwilling to share the information. The same pragmatic failure by a non-native speaker, however, was taken as a sign of inability to produce the necessary information (Exp. 1), even when participants were not explicitly informed that the non-native speaker could experience language difficulties (Exp. 2). Further, this 'forgiveness' for underinformative statements had consequences for participants' subsequent behaviours: They were more likely to learn new information from a previously encountered underinformative non-native speaker than from a native speaker (Exp. 3 and 4). One potential explanation is that non-native speakers are evaluated differently from native speakers due to the expectations listeners have about their competence: Non-native speakers' accents may invoke stereotypes whereby these speakers are believed to be less competent than native speakers [@levari2015; @fairchildpapafragou2018]. This expectation-based account proposes that stereotypes of non-native speakers' low linguistic competence affect both how their speech is comprehended and interpreted. Specifically, signs that can be attributed to low linguistic competence would be interpreted as such when produced by a non-native speaker and be attributed to other factors when produced by a native speaker. In line with this hypothesis, a speaker's nativeness affects how ironic a statement is perceived to be [@caffarraetal2018; @bazzietal2022], why a statement is believed to be underinformative [@fairchildpapafragou2018; @lorenzonietal2022; @ippapafragou2022] and why non-native speech is processed shallower [@levarikeysar2012; @hanulikovetal2012].

Thus far, the expectations-based account has explained findings pertaining how the content of speech is interpreted. However, stereotypes on linguistic competence may also affect how speech is expected to be delivered. In the case of confidence and knowledgeability, nativeness has been shown to affect how confidence conveyed by a voice is perceived [@jiangetal2019; @caballeropell2020]. Given that speakers producing speech in their second language are more disfluent [@bergmannetal2015; @davies2003; @gkalitsiouwerle2023] and is perceived as such by native listeners [@pingetetal2014], it could be possible that a speaker's nativeness leads to different interpretations of disfluencies. This would align with findings in the disfluency literature whereby the effects of those in speech comprehension are dependent on who produces it [@arnoldetal2007; @helleretal2015; @barrseyfeddinipur2010], including speaker's nativeness [@boskeretal2014], allegedly because listeners are sensitive to the speaker's mental state and the reasons for them to be disfluent.

@@

Listeners can infer speaker's knowledgeability from a range of cues, such as voice pitch or amplitude. A speaker's speech fluency i.e., whether they produces disfluencies as they speak, has been previously shown to impact how confident in their knowledge a speaker is judged to be [@brennanwilliams1995]. However, speakers can be disfluent for reasons other than (un)confidence: For example, speaking in own's second language is also associated with an increase in disfluencies [@dejongetal2015;@derwingetal2009]. In fact, it has been proposed that second language speakers are stereotyped and thus expected to display low linguistic performance [@levari2015], which consequently leads native listeners to "forgive" what otherwise would be lead to a negative evaluation [@lorenzonietal2022; @fairchildetal2020]. In the present experiment, we explored whether attributions of (un)knowledgeability as a function of the speaker's nativeness, and if those affected listeners' subsequent behaviours in a task where participants had to place bets on horse. Our findings suggest that manner of delivery, in the form of fluency, was the sole factor that guided participants' behavior: Disfluent descriptions yielded lower bets, regardless of who was speaking.

>>>>

Impressions of other people arise naturally and automatically [@ulemanetal2008]. Speakers can be evaluated not only by what they say but also by how they say it. For example, vocal features of speech can affect perceptions of confidence and persuasion [@guyeretal2019speech], status and solidarity [@pittamgallois198], or even attractiveness [@feinbergetal2005]. One speech feature consistently found to bias evaluations of the speaker is speech fluency. Disfluencies, such as _uh_ or _um_ in English, can lead to poorer evaluations of the speaker in terms of intelligence [@christenfeld1995], competence [@nortonhogan1980], and certainty of their own knowledge [@brennanwilliams1995]. Interestingly, speech produced with an accent different from one's own - particularly a _foreign_ accent - can also elicit negative perceptions of the speaker, including worse evaluations in terms of status, solidarity, and credibility [@gluszeketal2011; @gluszekdovidio2010; @rakicetal2011; @levarikeysar2010]. In this study, however, we explore a rather counterintuitive idea: That the co-presence of these two factors (i.e., (dis)fluency and foreign accents) can diminish the negative impact they have individually. It is important to note that we are not interested whether these cues correlate with a speaker's knowledge or whether listeners believe the speaker to be intentionally misleading: Rather, we are interested in whether, in scenarios where the speaker is expected to be cooperative and knowledgeable, listeners are still biased by irrelevant cues.

There is a growing body of literature showing that certain speech features impact listeners' perceptions of a speaker's knowledgeability. Voices with a slow speech rate, low amplitude, and a large F0 range are less likely to be rated as confident, and produce distinct neural responses [@jiangpell2015; @jiangpell2016a; @jiangpell2016b]. Similarly, prosody guides listeners' evaluations of certainty and honesty cross-linguistically [@goupiletal2021]. These non-verbal qualities of speech may be accompanied by verbal markers of hesitation, such as disfluencies [@shribergetal1997; @shriberglickley1993; @grosjeandeschamps1975; @jiangpell2017]. @brennanwilliams1995 demonstrated that filled pauses (e.g., uh, mm, or um) impact the perception of speakers’ confidence in their knowledge. In their study, participants listened to previously recorded answers to trivia questions (without hearing the questions) and were asked to rate how likely each speaker would be to recognise the correct answer to the question i.e., _feeling of another's knowing_, FOAK. Among the cues that biased participants' assessments were filled pauses:  Answers containing a disfluency were more likely to receive lower FOAK ratings, suggesting that filled pauses were taken as reflective of speakers’ reduced certainty about their knowledge. In contrast, non-answers (i.e., 'I don't know') were more likely to receive a higher FOAK rating if preceded by a filled pause. @brennanwilliams1995 took this as evidence that listeners are sensitive to the surface form of delivery, and in particular, to the cues displayed by speakers when they do not know (or cannot remember at the moment of being asked) the answer to a question [see also @smithclark1993].

Interestingly, speaker identity can itself affect evaluations of both the speaker and the content of speech. In particular, a speaker's nativeness (whether they are producing speech in their first or second language) has been consistently reported to elicit different evaluations. On the one hand, speakers with an accent different from that of the listeners are more likely to be negatively evaluated [e.g., @dragojevicgiles2016; @gluszekdovidio2010]. Statements produced with a foreign accent are more likely to receive lower ratings of credibility compared to statements produced with a native accent [@levarikeysar2010; @boduchlevari2021; but cf., @stocker2017; @wetzeletal2021; @barlowetal2024; @souzamarkman2013; @foucartetal2020; @foucarthartsuiker2021]. These negative effects of triggered by a speaker's non-nativeness have been accounted for in terms of processing fluency [@levarikeysar2010], group membership, and a combination of both [@maihoffmann2014].

On the other hand, there seem to be instances where being a non-native speaker is more advantageous. @fairchildetal2020 examined whether and how underinformativeness is interpreted differently as a function of speakers' nativeness. @fairchildetal2020 isolated the processing fluency component by presenting written stimuli, so that any differences in attributions were solely guided by speakers' identity. In a series of four experiments, participants read stories where a speaker (native/non-native) described a new invention. Native speakers who were underinformative were more likely to be rated as unwilling to share the information. The same pragmatic failure by a non-native speaker, however, was taken as a sign of inability to produce the necessary information (Exp. 1), even when participants were not explicitly informed that the non-native speaker could experience language difficulties (Exp. 2). Further, this 'forgiveness' for underinformative statements had consequences for participants' subsequent behaviours: They were more likely to learn new information from a previously encountered underinformative non-native speaker than from a native speaker (Exp. 3 and 4) [for similar results, see @@fairchildpapafragou2018; @lorenzonietal2022]. Interestingly, this pattern of results holds even for auditory stimuli [@ippapafragou2022], suggesting that difficulties in comprehending non-native-accented speech alone do not necessarily lead to negative evaluations of the speaker.

One potential explanation is that non-native speakers are evaluated differently from native speakers due to the expectations about their competence. Non-native speakers' accents may invoke stereotypes whereby these speakers are believed to be less competent than native speakers [@levari2015; @fairchildpapafragou2018]. This expectation-based account proposes that stereotypes of non-native speakers' low linguistic competence affect both how their speech is comprehended and interpreted. Specifically, signs that can be attributed to low linguistic competence would be interpreted as such when produced by a non-native speaker and be attributed to other factors when produced by a native speaker. In line with this hypothesis, a speaker's nativeness affects how ironic a statement is perceived to be [@caffarraetal2018; @bazzietal2022] or why non-native speech is processed more shallowly [@levarikeysar2012; @hanulikovetal2012].

Interestingly, stereotypes on linguistic competence may also affect how speech is expected to be delivered. For example, a speaker's nativeness has been shown to affect how confident a voice is perceived to be [@jiangetal2019; @caballeropell2020]. Given that speakers producing speech in their second language are more disfluent [@bergmannetal2015; @davies2003; @gkalitsiouwerle2023] and are perceived as such by native listeners [@pingetetal2014], it could be possible that a speaker's nativeness leads to different interpretations of disfluencies. This would align with findings in the disfluency literature whereby the effects of disfluencies in speech comprehension are dependent on who produces them [@arnoldetal2007; @helleretal2015; @barrseyfeddinipur2010], including speaker's nativeness [@boskeretal2014], allegedly because listeners are sensitive to the speaker's mental state and the reasons for being disfluent.

@@

Listeners can attribute a speaker knowledgeability based on a range of cues, such as voice pitch or amplitude. Speech (dis)fluency has been previously shown to impact how confident in their knowledge a speaker is judged to be [@brennanwilliams1995]. However, speakers can be disfluent for reasons other than (un)confidence: For example, speaking in one's second language is also associated with an increase in disfluencies [@dejongetal2015;@derwingetal2009]. In fact, it has been proposed that second language speakers are stereotyped and thus expected to display low linguistic performance [@levari2015], which consequently leads native listeners to "forgive" what otherwise would be lead to a negative evaluation [@lorenzonietal2022; @fairchildetal2020]. In the present experiment, we explored whether attributions of (un)knowledgeability as a function of the speaker's nativeness, and if those affected listeners' subsequent behaviours in a task where participants had to place bets on horse. Our findings suggest that manner of delivery, in the form of fluency, was the sole factor that guided participants' behavior: Disfluent descriptions yielded lower bets, regardless of who was speaking.

### 2024-09-16 manuscript/manuscript_eb.tex
change typos
there will still be typos :)

Impressions of other people arise naturally and automatically (Uleman, Adil Saribay, \& Gonzalez, 2008). Speakers can be evaluated not only by what they say but how they say it. For example, vocal features of speech can affect perceptions of confidence and persuasion (Guyer, Fabrigar, \& Vaughan-Johnston, 2019), status and solidarity (Pittam \& Gallois, 1986), and even attractiveness (Feinberg, Jones, Little, Burt, \& Perrett, 2005). One repeatedly reported feature of speech said to bias listeners' evaluations is its fluency. Disfluencies, such as \emph{uh} or \emph{um} in English can lead to poorer evaluations of the speaker in terms of intelligence (Christenfeld, 1995), competence (Norton-Ford \& Hogan, 1980), and certainty of their own knowledge (Brennan \& Williams, 1995). Interestingly, speech produced with an accent different from one's own - particularly a \emph{foreign} accent - can also elicit negative perceptions of the speaker, including worse evaluations in terms of status, solidarity, and credibility (Gluszek \& Dovidio, 2010; Gluszek, Newheiser, \& Dovidio, 2011; Lev-Ari \& Keysar, 2010; Rakić, Steffens, \& Mummendey, 2011). In this study, however, we explore a rather counterintuitive idea: That the co-presence of these two factors (i.e., (dis)fluency and foreign accents) can diminish the negative impact they have individually. It is important to note that it is not our interested whether these cues correlate with a speaker's knowledge or whether listeners believe the speaker to be intentionally misleading: Rather, we are interested in whether, in scenarios where the speaker is expected to be cooperative and knowledgeable, listeners are still biased by irrelevant cues.

There is a growing body of literature showing that listeners speech qualities are taken as reflective of a speaker's knowledgeability. Voices with a slow speech rate, low amplitude and a large F0 range are more likely to be rated as less confident, and produce distinct neural responses (Jiang \& Pell, 2015, 2016b, 2016a). Similarly, prosody guides listeners' evaluations of certainty and honesty cross-linguistically (Goupil, Ponsot, Richardson, Reyes, \& Aucouturier, 2021). These non-verbal qualities of speech may be accompanied by verbal markers of hesitation, such as disfluencies (Grosjean \& Deschamps, 1975; Jiang \& Pell, 2017; Shriberg, Bates, \& Stolcke, 1997; Shriberg \& Lickley, 1993). Brennan and Williams (1995) demonstrated that filled pauses (e.g., uh, mm, or um) can be perceived as indices of speakers' confidence in their knowledge. In their study, participants listened to previously recorded answers to trivia questions (without hearing the questions) and were asked to rate how likely each speaker would be to recognise the correct answer to the question i.e., \emph{feeling of another's knowing}, FOAK. Amongst the cues that biased participants' assessments were filled pauses: Answers containing a disfluency were more likely to receive lower FOAK ratings, suggesting that filled pauses were taken as reflective of speakers' reduced certainty about their knowledge. In contrast, non-answers (i.e., `I don't know') were more likely to receive a higher FOAK rating if preceded by a filled pause. Brennan and Williams (1995) took this as evidence that listeners are sensitive to the surface form of delivery, and in particular, to the cues displayed by speakers when they do not know (or cannot remember at the moment of being asked) the answer to a question (see also Smith \& Clark, 1993).

Interestingly, who produces the information can also affect how it is evaluated. On the one hand, speakers with an accent different from that of the listeners are more likely to be negatively evaluated (e.g., (Dragojevic \& Giles, 2016; Gluszek \& Dovidio, 2010) and statements produced with a foreign-accent are more likely to receive lower ratings of credibility compared to statements produced with a native accent (Boduch-Grabka \& Lev-Ari, 2021; Lev-Ari \& Keysar, 2010; Barlow et al., 2024; Foucart, Costa, Morís-Fernández, \& Hartsuiker, 2020; Foucart \& Hartsuiker, 2021; Souza \& Markman, 2013; but cf., Stocker, 2017; Wetzel, Zufferey, \& Gygax, 2021). This divide in evaluations as a function of a speaker's accent has been accounted for in terms of processing fluency (Lev-Ari \& Keysar, 2010), group membership, and a combination of both (Mai \& Hoffmann, 2013).

Alternatively, but not exclusively, speaker identity in itself can bias interpretation. Specifically, whether a speaker is providing information in their first or second language has been shown to affect that listeners interpret. Fairchild, Mathis, and Papafragou (2020) asked participants to explain why a native or a non-native speaker had been underinformative in a previously presented story. Native speakers who provided less information than necessary were more likely to be rated as unwilling to share the information. The same pragmatic failure by a non-native speaker, however, was taken as a sign of inability to produce the necessary information (Exp. 1), even when participants were not explicitly informed that the non-native speaker could experience language difficulties (Exp. 2). Further, this `forgiveness' for underinformative statements had consequences for participants' subsequent behaviours: They were more likely to learn new information from a previously encountered underinformative non-native speaker than from a native speaker (Exp. 3 and 4). One potential explanation is that non-native speakers are evaluated differently from native speakers due to the expectations listeners have about their competence: Non-native speakers' accents may invoke stereotypes whereby these speakers are believed to be less competent than native speakers (Fairchild \& Papafragou, 2018; Lev-Ari, 2015). This expectation-based account proposes that stereotypes of non-native speakers' low linguistic competence affect both how their speech is comprehended and interpreted. Specifically, signs that can be attributed to low linguistic competence would be interpreted as such when produced by a non-native speaker and be attributed to other factors when produced by a native speaker. In line with this hypothesis, a speaker's nativeness affects how ironic a statement is perceived to be (Bazzi, Brouwer, \& Foucart, 2022; Caffarra, Michell, \& Martin, 2018), why a statement is believed to be underinformative (Fairchild \& Papafragou, 2018; Ip \& Papafragou, 2022; Lorenzoni, Pagliarini, Vespignani, \& Navarrete, 2022) and why non-native speech is processed shallower (Hanuíková, Alphen, Goch, \& Weber, 2012; Lev-Ari \& Keysar, 2012).

Thus far, the expectations-based account has explained findings pertaining how the content of speech is interpreted. However, stereotypes on linguistic competence may also affect how speech is expected to be delivered. In the case of confidence and knowledgeability, nativeness has been shown to affect how confidence conveyed by a voice is perceived (Caballero \& Pell, 2020; Jiang, Gossack-Keenan, \& Pell, 2019). Given that speakers producing speech in their second language are more disfluent (Bergmann, Sprenger, \& Schmid, 2015; Davies, 2003; Gkalitsiou \& Werle, 2023) and is perceived as such by native listeners (Pinget, Bosker, Quené, \& De Jong, 2014), it could be possible that a speaker's nativeness leads to different interpretations of disfluencies. This would align with findings in the disfluency literature whereby the effects of those in speech comprehension are dependent on who produces it (Arnold, Kam, \& Tanenhaus, 2007; Barr \& Seyfeddinipur, 2010; Heller, Arnold, Klein, \& Tanenhaus, 2015), including speaker's nativeness (Bosker, Quené, Sanders, \& De Jong, 2014), allegedly because listeners are sensitive to the speaker's mental state and the reasons for them to be disfluent.

@@

Listeners can infer speaker's knowledgeability from a range of cues, such as voice pitch or amplitude. A speaker's speech fluency i.e., whether they produces disfluencies as they speak, has been previously shown to impact how confident in their knowledge a speaker is judged to be (Brennan \& Williams, 1995). However, speakers can be disfluent for reasons other than (un)confidence: For example, speaking in own's second language is also associated with an increase in disfluencies (De Jong, Groenhout, Schoonen, \& Hulstijn, 2015; Derwing, Munro, Thomson, \& Rossiter, 2009). In fact, it has been proposed that second language speakers are stereotyped and thus expected to display low linguistic performance (Lev-Ari, 2015), which consequently leads native listeners to ``forgive'' what otherwise would be lead to a negative evaluation (Fairchild et al., 2020; Lorenzoni et al., 2022). In the present experiment, we explored whether attributions of (un)knowledgeability as a function of the speaker's nativeness, and if those affected listeners' subsequent behaviours in a task where participants had to place bets on horse. Our findings suggest that manner of delivery, in the form of fluency, was the sole factor that guided participants' behavior: Disfluent descriptions yielded lower bets, regardless of who was speaking.

>>>>

Impressions of other people arise naturally and automatically (Uleman, Adil Saribay, \& Gonzalez, 2008). Speakers can be evaluated not only by what they say but also by how they say it. For example, vocal features of speech can affect perceptions of confidence and persuasion (Guyer, Fabrigar, \& Vaughan-Johnston, 2019), status and solidarity (Pittam \& Gallois, 1986), or even attractiveness (Feinberg, Jones, Little, Burt, \& Perrett, 2005). One speech feature consistently found to bias evaluations of the speaker is speech fluency. Disfluencies, such as \emph{uh} or \emph{um} in English, can lead to poorer evaluations of the speaker in terms of intelligence (Christenfeld, 1995), competence (Norton-Ford \& Hogan, 1980), and certainty of their own knowledge (Brennan \& Williams, 1995). Interestingly, speech produced with an accent different from one's own - particularly a \emph{foreign} accent - can also elicit negative perceptions of the speaker, including worse evaluations in terms of status, solidarity, and credibility (Gluszek \& Dovidio, 2010; Gluszek, Newheiser, \& Dovidio, 2011; Lev-Ari \& Keysar, 2010; Rakić, Steffens, \& Mummendey, 2011). In this study, however, we explore a rather counterintuitive idea: That the co-presence of these two factors (i.e., (dis)fluency and foreign accents) can diminish the negative impact they have individually. It is important to note that we are not interested whether these cues correlate with a speaker's knowledge or whether listeners believe the speaker to be intentionally misleading: Rather, we are interested in whether, in scenarios where the speaker is expected to be cooperative and knowledgeable, listeners are still biased by irrelevant cues.

There is a growing body of literature showing that certain speech features impact listeners' perceptions of a speaker's knowledgeability. Voices with a slow speech rate, low amplitude, and a large F0 range are less likely to be rated as confident, and produce distinct neural responses (Jiang \& Pell, 2015, 2016b, 2016a). Similarly, prosody guides listeners' evaluations of certainty and honesty cross-linguistically (Goupil, Ponsot, Richardson, Reyes, \& Aucouturier, 2021). These non-verbal qualities of speech may be accompanied by verbal markers of hesitation, such as disfluencies (Grosjean \& Deschamps, 1975; Jiang \& Pell, 2017; Shriberg, Bates, \& Stolcke, 1997; Shriberg \& Lickley, 1993). Brennan and Williams (1995) demonstrated that filled pauses (e.g., uh, mm, or um) impact the perception of speakers' confidence in their knowledge. In their study, participants listened to previously recorded answers to trivia questions (without hearing the questions) and were asked to rate how likely each speaker would be to recognise the correct answer to the question i.e., \emph{feeling of another's knowing}, FOAK. Among the cues that biased participants' assessments were filled pauses: Answers containing a disfluency were more likely to receive lower FOAK ratings, suggesting that filled pauses were taken as reflective of speakers' reduced certainty about their knowledge. In contrast, non-answers (i.e., `I don't know') were more likely to receive a higher FOAK rating if preceded by a filled pause. Brennan and Williams (1995) took this as evidence that listeners are sensitive to the surface form of delivery, and in particular, to the cues displayed by speakers when they do not know (or cannot remember at the moment of being asked) the answer to a question (see also Smith \& Clark, 1993).

Interestingly, speaker identity can itself affect evaluations of both the speaker and the content of speech. In particular, a speaker's nativeness (whether they are producing speech in their first or second language) has been consistently reported to elicit different evaluations. On the one hand, speakers with an accent different from that of the listeners are more likely to be negatively evaluated (e.g., Dragojevic \& Giles, 2016; Gluszek \& Dovidio, 2010). Statements produced with a foreign accent are more likely to receive lower ratings of credibility compared to statements produced with a native accent (Boduch-Grabka \& Lev-Ari, 2021; Lev-Ari \& Keysar, 2010; Barlow et al., 2024; Foucart, Costa, Morís-Fernández, \& Hartsuiker, 2020; Foucart \& Hartsuiker, 2021; Souza \& Markman, 2013; but cf., Stocker, 2017; Wetzel, Zufferey, \& Gygax, 2021). These negative effects of triggered by a speaker's non-nativeness have been accounted for in terms of processing fluency (Lev-Ari \& Keysar, 2010), group membership, and a combination of both (Mai \& Hoffmann, 2013).

On the other hand, there seem to be instances where being a non-native speaker is more advantageous. Fairchild, Mathis, and Papafragou (2020) examined whether and how underinformativeness is interpreted differently as a function of speakers' nativeness. Fairchild et al. (2020) isolated the processing fluency component by presenting written stimuli, so that any differences in attributions were solely guided by speakers' identity. In a series of four experiments, participants read stories where a speaker (native/non-native) described a new invention. Native speakers who were underinformative were more likely to be rated as unwilling to share the information. The same pragmatic failure by a non-native speaker, however, was taken as a sign of inability to produce the necessary information (Exp. 1), even when participants were not explicitly informed that the non-native speaker could experience language difficulties (Exp. 2). Further, this `forgiveness' for underinformative statements had consequences for participants' subsequent behaviours: They were more likely to learn new information from a previously encountered underinformative non-native speaker than from a native speaker (Exp. 3 and 4) (for similar results, see @ Fairchild \& Papafragou, 2018; Lorenzoni, Pagliarini, Vespignani, \& Navarrete, 2022). Interestingly, this pattern of results holds even for auditory stimuli (Ip \& Papafragou, 2022), suggesting that difficulties in comprehending non-native-accented speech alone do not necessarily lead to negative evaluations of the speaker.

One potential explanation is that non-native speakers are evaluated differently from native speakers due to the expectations about their competence. Non-native speakers' accents may invoke stereotypes whereby these speakers are believed to be less competent than native speakers (Fairchild \& Papafragou, 2018; Lev-Ari, 2015). This expectation-based account proposes that stereotypes of non-native speakers' low linguistic competence affect both how their speech is comprehended and interpreted. Specifically, signs that can be attributed to low linguistic competence would be interpreted as such when produced by a non-native speaker and be attributed to other factors when produced by a native speaker. In line with this hypothesis, a speaker's nativeness affects how ironic a statement is perceived to be (Bazzi, Brouwer, \& Foucart, 2022; Caffarra, Michell, \& Martin, 2018) or why non-native speech is processed more shallowly (Hanuíková, Alphen, Goch, \& Weber, 2012; Lev-Ari \& Keysar, 2012).

Interestingly, stereotypes on linguistic competence may also affect how speech is expected to be delivered. For example, a speaker's nativeness has been shown to affect how confident a voice is perceived to be (Caballero \& Pell, 2020; Jiang, Gossack-Keenan, \& Pell, 2019). Given that speakers producing speech in their second language are more disfluent (Bergmann, Sprenger, \& Schmid, 2015; Davies, 2003; Gkalitsiou \& Werle, 2023) and are perceived as such by native listeners (Pinget, Bosker, Quené, \& De Jong, 2014), it could be possible that a speaker's nativeness leads to different interpretations of disfluencies. This would align with findings in the disfluency literature whereby the effects of disfluencies in speech comprehension are dependent on who produces them (Arnold, Kam, \& Tanenhaus, 2007; Barr \& Seyfeddinipur, 2010; Heller, Arnold, Klein, \& Tanenhaus, 2015), including speaker's nativeness (Bosker, Quené, Sanders, \& De Jong, 2014), allegedly because listeners are sensitive to the speaker's mental state and the reasons for being disfluent.

@@

Listeners can attribute a speaker knowledgeability based on a range of cues, such as voice pitch or amplitude. Speech (dis)fluency has been previously shown to impact how confident in their knowledge a speaker is judged to be (Brennan \& Williams, 1995). However, speakers can be disfluent for reasons other than (un)confidence: For example, speaking in one's second language is also associated with an increase in disfluencies (De Jong, Groenhout, Schoonen, \& Hulstijn, 2015; Derwing, Munro, Thomson, \& Rossiter, 2009). In fact, it has been proposed that second language speakers are stereotyped and thus expected to display low linguistic performance (Lev-Ari, 2015), which consequently leads native listeners to ``forgive'' what otherwise would be lead to a negative evaluation (Fairchild et al., 2020; Lorenzoni et al., 2022). In the present experiment, we explored whether attributions of (un)knowledgeability as a function of the speaker's nativeness, and if those affected listeners' subsequent behaviours in a task where participants had to place bets on horse. Our findings suggest that manner of delivery, in the form of fluency, was the sole factor that guided participants' behavior: Disfluent descriptions yielded lower bets, regardless of who was speaking.
